Synthesis of Linear Functional Programs

### 2021-07-23 article/article.tex
remove lambdas unicode

bind :: forall a b c . (State c a -o ((a -o State c b) -o State c b));
bind bs bt = case bs of
    State bu ->
      State (λbv -> let !bw = bv in
                      let cu*cv = bu (!bw) in
                        let !cw = cv in
                          (let dr*ds = runState (bt cu) (!cw) in
                             let !dt = ds in dr, (!cw)));

return :: forall a b . (a -o State b a);
return c = State (λd -> let !e = d in
               (c, (!e)));

get :: forall a . State a a;
get = State (λb -> let !c = b in
               (c, (!c)));

put :: forall a . (!a -o State a 1);
put b = let !c = b in
  State (λd -> let !e = d in
                 ((), (!e)));

modify :: forall a . ((!a -o !a) -o State a 1);
modify b = State (λc -> let !d = c in
               let !f = b (!d) in ((), (!f)));

>>>>

bind :: forall a b c . (State c a -o ((a -o State c b) -o State c b));
bind bs bt = case bs of
    State bu ->
      State (\bv -> let !bw = bv in
                      let cu*cv = bu (!bw) in
                        let !cw = cv in
                          (let dr*ds = runState (bt cu) (!cw) in
                             let !dt = ds in dr, (!cw)));

return :: forall a b . (a -o State b a);
return c = State (\d -> let !e = d in
               (c, (!e)));

get :: forall a . State a a;
get = State (\b -> let !c = b in
               (c, (!c)));

put :: forall a . (!a -o State a 1);
put b = let !c = b in
  State (\d -> let !e = d in
                 ((), (!e)));

modify :: forall a . ((!a -o !a) -o State a 1);
modify b = State (\c -> let !d = c in
               let !f = b (!d) in ((), (!f)));
